### 2021-06-01 papers/thesis/full/ch2-spherical-harmonics/spherical-harmonics.tex
Fig sizes changed to be consistent and bigger.
Spacing and margins of SH chapter eqns fixed.

For each $l = 0,1,2\dots$ let $\Dlt$ be any matrix that is a left inverse of $A_l$, i.e. such that $\Dlt A_l = \idmat{2l+3}$. Multiplying our system by the preconditioner matrix that is given by the block diagonal matrix of the $\Dlt$'s, we obtain a lower triangular system \cite[Section 3.2]{dunkl2014orthogonal}, which can be expanded to obtain the three-term recurrence:
\bseqn{
	\begin{cases}
		\SHvec_{-1}(x,y,z) := 0 \\
		\SHvec_{0}(x,y,z) := Y_0 \\
		\SHvec_{l+1}(x,y,z) = -\Dlt (B_l-G_l(x,y,z)) \SHvec_l(x,y,z) - \Dlt C_l  \,\SHvec_{l-1}(x,y,z), \quad l = 0,1,2,\dots.
	\end{cases}
}

@@

	Fix $l \in \N$ and $m \in \Z$ s.t. $-l \le m \le l$. The proof we will use is to directly calculate the nonzero coefficients in each expansion using inner products. To this end, note that
\bseqn{
	x \gradYlm = \sum_{l'=1}^{l+1} \sum_{m'=-l'}^{l'} \calA_{l',m'} \gradYlmprime + \calA^\perp_{l',m'} \gradpYlmprime
}
where the coefficients are given by
\bseqn{
	\calA_{l',m'} = {\ip<x \gradYlm, \gradYlmprime> \over \norm{\gradYlmprime}^2} = {1 \over l'(l'+1)} \ip<x \gradYlm, \gradYlmprime> \\
	\calA^\perp_{l',m'} = {\ip<x \gradYlm, \gradpYlmprime> \over \norm{\gradpYlmprime}^2} = {1 \over l'(l'+1)} \ip<x \gradYlm, \gradpYlmprime>.
}
The aim will be to show that the only nonzero coefficients $\calA_{l',m'}$, $\calA^\perp_{l',m'}$ match the $A_{l,m,j}$ for $j=1,\dots,6$ in the Lemma. Now, using a change of variable, we have that
\bseqnnumber{
	&\ip<x \gradYlm, \gradYlmprime> \nonumber \\
	&= \iint_\Omega \costheta \sinphi \: \gradYlm \cdot {\gradYlmprime}^* \sinphi \: \D\phi \: \D\theta \nonumber \\
	&= \clm \clmprime \Big( \int_0^{2pi} \eimtheta \eimthetaprime \costheta \: \D\theta \Big) \nonumber \\
	&\quadfour \cdot \Big( \int_{-1}^{1} \Big\{ \big[ \abs{m} z \jaclmabs{l}{m}(z) - \rho(z)^2 \jaclmabsdz{l}{m}(z) \big] \big[ \abs{m'} z \jaclmabs{l'}{m'}(z) - \rho(z)^2 \jaclmabs{l'}{m'}(z) \big] \nonumber \\
	&\quadeight + mm' \jaclmabs{l}{m}(z) \jaclmabs{l'}{m'}(z) \Big\} \: \rho(z)^{\abs{m}+\abs{m'}-1} \: \D z \Big) \nonumber \\
	&= \clm \clmprime \pi (\delta_{m',m-1} + \delta_{m',m+1}) \nonumber \\
	&\quadfour \cdot \Big( \int_{-1}^{1} \Big\{ \jaclmabs{l}{m} \jaclmabs{l'}{m'} \rho^{\abs{m}+\abs{m'}-1} \big(mm' + \abs{m}\abs{m'} z^2 \big) \nonumber \\
	&\quadeight - \abs{m} z \jaclmabs{l}{m} \jaclmabsdz{l'}{m'} \rho^{\abs{m}+\abs{m'}+1} \nonumber \\
	&\quadeight - \abs{m'} z \jaclmabsdz{l}{m} \jaclmabs{l'}{m'} \rho^{\abs{m}+\abs{m'}+1} \nonumber  \\
	&\quadeight + \jaclmabsdz{l}{m} \jaclmabsdz{l'}{m'} \rho^{\abs{m}+\abs{m'}+3} \Big\} \: \D z \Big). \label{eqn:lemmaVSHrecurrencesproof}
}
We can conclude that the only possible nonzero coefficients are when $m' = m \pm 1$, and so it is left to evaluate the integral that is left at \bsrefeqn{eqn:lemmaVSHrecurrencesproof} when $m'$ takes either value. Since we need to take account of the fact that $m$ can be negative, to simplify our argument we make use of the fact that $m' = m - 1$ for $m < 0$ is analogous to the case $m' = m+1$ for $m > 0$, and vice versa.

On that note, we will first consider the case that $m > 0$ and $m' = m - 1$, and calculate the integral in \bsrefeqn{eqn:lemmaVSHrecurrencesproof}:
\bseqnnumber{
	&\int_{-1}^{1} \Big\{ m(m-1) \jaclm{l}{m} \jaclmbracket{l'}{m-1} \rho^{2m-2} (1 + z^2) - m z \jaclm{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m} \nonumber \\
	&\quadtwo \quad - (m-1) z \jaclmdz{l}{m} \jaclmbracket{l'}{m-1} \rho^{2m} + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ m(m-1) \jaclm{l}{m} \jaclmbracket{l'}{m-1} \rho^{2m-2} (1 + z^2) - m z \jaclm{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m} \nonumber \\
	&\quadfour + (m-1) \jaclm{l}{m} \rho^{2m-2} \big( - 2m z^2 \jaclmbracket{l'}{m-1} + \jaclmbracket{l'}{m-1} \rho^{2} - z \jaclmbracketdz{l'}{m-1} \rho^{2} \big) \nonumber \\
	&\quadfour + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ (m-1)(m+1) \jaclm{l}{m} \jaclmbracket{l'}{m-1} \rho^{2m} - z \jaclm{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m} \nonumber \\
	&\quadfour + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ (m-1)(m+1) \jaclm{l}{m} \jaclmbracket{l'}{m-1} \rho^{2m} - d_{l',m-1} z \jaclm{l}{m} \jaclm{l'}{m} \rho^{2m} \nonumber \\
	&\quadfour + d_{l,m} d_{l',m-1} \jaclmbracket{l}{m+1} \jaclm{l'}{m} \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ (m^2 - 1) \jaclm{l}{m} \big( \tilde \alpha_{l', m-1, 2} \jaclm{l'-1}{m} + \tilde \alpha_{l', m-1, 4} \jaclm{l'+1}{m} \big) \rho^{2m} \nonumber \\
	&\quadfour - d_{l',m-1} \jaclm{l}{m} \big( \tilde \gamma_{l',m,1} \jaclm{l'-1}{m} + \tilde \gamma_{l',m,2} \jaclm{l'+1}{m} \big) \rho^{2m} \nonumber \\
	&\quadfour + d_{l,m} d_{l',m-1} \jaclm{l'}{m} \big( \tilde \alpha_{l, m+1, 1} \jaclm{l-1}{m} + \tilde \alpha_{l, m+1, 3} \jaclm{l+1}{m} \big) \rho^{2m} \Big\} \: \D z \nonumber \\
	&= \delta_{l',l-1} \Big( \big[ (m^2 - 1) \tilde \alpha_{l-1, m-1, 4} - d_{l-1,m-1} \tilde \gamma_{l-1,m,2} \big] {1\over2\pi(\clm)^2} + d_{l,m} d_{l-1,m-1} {\tilde \alpha_{l-1, m-1, 1} \over 2\pi (c_{l-1}^m)^2} \Big) \nonumber \\
	&\quadtwo + \delta_{l',l+1} \Big( \big[ (m^2 - 1) \tilde \alpha_{l+1, m-1, 2} - d_{l+1,m-1} \tilde \gamma_{l+1,m,1} \big] {1\over2\pi(\clm)^2} + d_{l,m} d_{l+1,m-1} {\tilde \alpha_{l-1, m-1, 3} \over 2\pi (c_{l+1}^m)^2} \Big). \label{eqn:lemmaVSHrecurrencesproof2}
}
As we can see, the coefficients are then also only possibly nonzero for $l' = l \pm 1$. Combining the above with the \bsrefeqn{eqn:lemmaVSHrecurrencesproof}, we have that our two coefficients for $\calA_{l-1,m-1}, \calA_{l+1,m-1}$ are those stated in the Lemma as $A_{l,m,1}$ and $A_{l,m,3}$, for $m > 0$.

Next, assume $m \ge 0$ and consider the case $m' = m + 1$. The integral in \bsrefeqn{eqn:lemmaVSHrecurrencesproof} is then:
\bseqnnumber{
	&\int_{-1}^{1} \Big\{ m(m+1) \jaclm{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m} (1 + z^2) - m z \jaclm{l}{m} \jaclmbracketdz{l'}{m+1} \rho^{2m+2} \nonumber \\
	&\quadtwo \quad - (m+1) z \jaclmdz{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m+2} + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m+1} \rho^{2m+4} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ m(m+1) \jaclm{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m} (1 + z^2) - (m+1) z \jaclmdz{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m+2} \nonumber \\
	&\quadfour + m \jaclmbracket{l'}{m+1} \rho^{2m} \big( - 2(m+1) z^2 \jaclm{l}{m} + \jaclm{l}{m} \rho^{2} - z \jaclmdz{l}{m} \rho^{2} \big) \nonumber \\
	&\quadfour + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m+1} \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ m(m+2) \jaclm{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m+2} - z \jaclmdz{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m+2} \nonumber \\
	&\quadfour + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m+1} \rho^{2m+4} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ m(m+2) \jaclm{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m+2} - d_{l,m} z \jaclmbracket{l}{m+1} \jaclmbracket{l'}{m+1} \rho^{2m+2} \nonumber \\
	&\quadfour + d_{l,m} d_{l',m+1} \jaclmbracket{l}{m+1} \jaclmbracket{l'}{m+2} \rho^{2m+4} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ m(m+2) \jaclmbracket{l'}{m+1} \big( \tilde \alpha_{l, m, 2} \jaclmbracket{l-1}{m+1} + \tilde \alpha_{l, m, 4} \jaclmbracket{l+1}{m+1} \big) \rho^{2m+2} \nonumber \\
	&\quadfour - d_{l,m} \jaclmbracket{l'}{m+1} \big( \tilde \gamma_{l,m+1,1} \jaclmbracket{l-1}{m+1} + \tilde \gamma_{l,m+1,2} \jaclmbracket{l+1}{m+1} \big) \rho^{2m+2} \nonumber \\
	&\quadfour + d_{l,m} d_{l',m+1} \jaclmbracket{l}{m+1} \big( \tilde \alpha_{l', m+2, 1} \jaclmbracket{l'-1}{m+1} + \tilde \alpha_{l', m+2, 3} \jaclmbracket{l'+1}{m+1}  \big) \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= \delta_{l',l-1} \Big( \big[ m(m+2) \tilde \alpha_{l, m, 2} - d_{l,m} \tilde \gamma_{l,m+1,1} \big] {1 \over 2 \pi (c_{l-1}^{m+1})^2} + d_{l,m} d_{l-1,m+1} {\tilde \alpha_{l-1, m+2, 3} \over 2\pi (c_{l}^{m+1})^2} \Big) \nonumber \\
	&\quadtwo + \delta_{l',l+1} \Big( \big[ m(m+2) \tilde \alpha_{l, m, 4} - d_{l,m} \tilde \gamma_{l,m+1,2} \big] {1 \over 2 \pi (c_{l-1}^{m+1})^2} + d_{l,m} d_{l+1,m+1} {\tilde \alpha_{l+1, m+2, 1} \over 2\pi (c_{l}^{m+1})^2} \Big). \label{eqn:lemmaVSHrecurrencesproof3}
}
Again, we can see that the coefficients are then also only possibly nonzero for $l' = l \pm 1$. Combining the above with the \bsrefeqn{eqn:lemmaVSHrecurrencesproof}, we have that our two coefficients for $\calA_{l-1,m-1}, \calA_{l+1,m-1}$ are those stated in the Lemma as $A_{l,m,2}$ and $A_{l,m,4}$, for $m \ge 0$.

@@

	&\quadfour \cdot \Big( \int_{-1}^{1} \Big\{ i m' \jaclmabs{l'}{m'}(z) \rho(z)^{\abs{m} + \abs{m'} - 1} \big[ \abs{m} z \jaclmabs{l}{m}(z) - \rho(z)^2 \jaclmabsdz{l}{m}(z) \big] \nonumber \\
	&\quadeight + i m \jaclmabs{l}{m}(z) \rho(z)^{\abs{m} + \abs{m'} - 1} \big[ \abs{m'} z \jaclmabs{l'}{m'}(z) - \rho(z)^2 \jaclmabs{l'}{m'}(z) \big] \Big\} \: \D z \Big) \nonumber \\

@@

	&\quadfour \cdot \Big( \int_{-1}^{1} \Big\{ \sgn{m} 2 i \, m \, m' \, z \jaclmabs{l}{m} \jaclmabs{l'}{m'} \rho^{\abs{m} + \abs{m'} - 1} \nonumber \\

@@

since when the above is nonzero, $m, m'$ will have the same sign (or one is zero) and so $\abs{m}m' + \abs{m'}m = \sgn{m}mm'$. Once again, we can conclude that $\calA^\perp_{l',m'}$ are zero for $m' \notin \{m-1, m+1\}$. It is left to evaluate the integral that is left at \bsrefeqn{eqn:lemmaVSHrecurrencesproof4} when $m'$ takes either $m\pm 1$ value. First, consider the case that $m > 0$ and $m' = m - 1$. The integral is then, using integration by parts:

@@

	&= \int_{-1}^{1} \Big\{ - 2 i \, m(m+1) \, z \jaclmabs{l}{m} \jaclmbracket{l'}{\abs{m} - 1} \rho^{2 \abs{m} - 2} - i m \jaclmabs{l}{m} \jaclmbracketdz{l'}{\abs{m} - 1} \rho^{2\abs{m}} \nonumber \\

@@

	&\quad \cdot \Big( \int_{-1}^{1} \Big\{ \big[ \abs{m} z \jaclmabs{l}{m}(z) - \rho(z)^2 \jaclmabsdz{l}{m}(z) \big] \big[ \abs{m'} z \jaclmabs{l'}{m'}(z) - \rho(z)^2 \jaclmabs{l'}{m'}(z) \big] \nonumber \\

@@

\begin{figure}[tp]
	\centering % <-- added
	\includegraphics[scale=0.5]{heat-eqn-alpha-0p0238-dt=0p01-nsteps=100}
	\caption{Four snapshots of the solution $u$ of the heat equation with $\alpha = 1/42$ and a step size of $\Delta t = 0.01$, solved using the BDF2 timestepping method. Top Left: Initial conditions (0 timesteps). Top Right: After 25 timesteps. Bottom Left: After 50 timesteps. Bottom Right: After 75 timesteps.}
	\label{fig:heateqn}
\end{figure}

@@

\begin{figure}[tp]
	\centering % <-- added
	\includegraphics[scale=0.5]{linear-swe-H=1-dt=0p01-nsteps=100}
	\caption{Four snapshots of the solution for the height $h$ of the linearised shallow water equations with $\rotrate = \calH = 1$ and a step size of $\Delta t = 0.01$, solved using the backwards Euler timestepping method. Top Left: Initial conditions (0 timesteps). Top Right: After 50 timesteps. Bottom Left: After 75 timesteps. Bottom Right: After 100 timesteps.}
	\label{fig:swe}
\end{figure}

>>>>

For each $l = 0,1,2\dots$ let $\Dlt$ be any matrix that is a left inverse of $A_l$, i.e. such that $\Dlt A_l = \idmat{2l+3}$. Multiplying our system by the preconditioner matrix that is given by the block diagonal matrix of the $\Dlt$'s, we obtain a lower triangular system \cite[Section 3.2]{dunkl2014orthogonal}, which can be expanded to obtain the three-term recurrence, for $l = 0,1,2,\dots$:
\bseqn{
	\begin{cases}
		\SHvec_{-1}(x,y,z) := 0 \\
		\SHvec_{0}(x,y,z) := Y_0 \\
		\SHvec_{l+1}(x,y,z) = -\Dlt (B_l-G_l(x,y,z)) \SHvec_l(x,y,z) - \Dlt C_l  \,\SHvec_{l-1}(x,y,z)
	\end{cases}
}

@@

	Fix $l \in \N$ and $m \in \Z$ s.t. $-l \le m \le l$. The proof we will use is to directly calculate the nonzero coefficients in each expansion using inner products. To this end, note that
\bseqn{
	x \gradYlm = \sum_{l'=1}^{l+1} \sum_{m'=-l'}^{l'} \calA_{l',m'} \gradYlmprime + \calA^\perp_{l',m'} \gradpYlmprime
}
where the coefficients are given by
\bseqn{
	\calA_{l',m'} = {\ip<x \gradYlm, \gradYlmprime> \over \norm{\gradYlmprime}^2} = {1 \over l'(l'+1)} \ip<x \gradYlm, \gradYlmprime> \\
	\calA^\perp_{l',m'} = {\ip<x \gradYlm, \gradpYlmprime> \over \norm{\gradpYlmprime}^2} = {1 \over l'(l'+1)} \ip<x \gradYlm, \gradpYlmprime>.
}
The aim will be to show that the only nonzero coefficients $\calA_{l',m'}$, $\calA^\perp_{l',m'}$ match the $A_{l,m,j}$ for $j=1,\dots,6$ in the Lemma. Now, using a change of variable, we have that
\bseqnnumber{
	&\ip<x \gradYlm, \gradYlmprime> \nonumber \\
	&= \iint_\Omega \costheta \sinphi \: \gradYlm \cdot {\gradYlmprime}^* \sinphi \: \D\phi \: \D\theta \nonumber \\
	&= \clm \clmprime \Big( \int_0^{2pi} \eimtheta \eimthetaprime \costheta \: \D\theta \Big) \nonumber \\
	&\quadfour \cdot \Big( \int_{-1}^{1} \Big\{ \big[ \abs{m} z \jaclmabs{l}{m}(z) - \rho(z)^2 \jaclmabsdz{l}{m}(z) \big] \nonumber \\
	&\quadeight \quadtwo \cdot \big[ \abs{m'} z \jaclmabs{l'}{m'}(z) - \rho(z)^2 \jaclmabs{l'}{m'}(z) \big] \nonumber \\
	&\quadeight + mm' \jaclmabs{l}{m}(z) \jaclmabs{l'}{m'}(z) \Big\} \: \rho(z)^{\abs{m}+\abs{m'}-1} \: \D z \Big) \nonumber \\
	&= \clm \clmprime \pi (\delta_{m',m-1} + \delta_{m',m+1}) \nonumber \\
	&\quadfour \cdot \Big( \int_{-1}^{1} \Big\{ \jaclmabs{l}{m} \jaclmabs{l'}{m'} \rho^{\abs{m}+\abs{m'}-1} \big(mm' + \abs{m}\abs{m'} z^2 \big) \nonumber \\
	&\quadeight - \abs{m} z \jaclmabs{l}{m} \jaclmabsdz{l'}{m'} \rho^{\abs{m}+\abs{m'}+1} \nonumber \\
	&\quadeight - \abs{m'} z \jaclmabsdz{l}{m} \jaclmabs{l'}{m'} \rho^{\abs{m}+\abs{m'}+1} \nonumber  \\
	&\quadeight + \jaclmabsdz{l}{m} \jaclmabsdz{l'}{m'} \rho^{\abs{m}+\abs{m'}+3} \Big\} \: \D z \Big). \label{eqn:lemmaVSHrecurrencesproof}
}
We can conclude that the only possible nonzero coefficients are when $m' = m \pm 1$, and so it is left to evaluate the integral that is left at \bsrefeqn{eqn:lemmaVSHrecurrencesproof} when $m'$ takes either value. Since we need to take account of the fact that $m$ can be negative, to simplify our argument we make use of the fact that $m' = m - 1$ for $m < 0$ is analogous to the case $m' = m+1$ for $m > 0$, and vice versa.

On that note, we will first consider the case that $m > 0$ and $m' = m - 1$, and calculate the integral in \bsrefeqn{eqn:lemmaVSHrecurrencesproof}:
\bseqnnumber{
	&\int_{-1}^{1} \Big\{ m(m-1) \jaclm{l}{m} \jaclmbracket{l'}{m-1} \rho^{2m-2} (1 + z^2) - m z \jaclm{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m} \nonumber \\
	&\quadtwo \quad - (m-1) z \jaclmdz{l}{m} \jaclmbracket{l'}{m-1} \rho^{2m} + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ m(m-1) \jaclm{l}{m} \jaclmbracket{l'}{m-1} \rho^{2m-2} (1 + z^2) - m z \jaclm{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m} \nonumber \\
	&\quadtwo + (m-1) \jaclm{l}{m} \rho^{2m-2} \big(\jaclmbracket{l'}{m-1} \rho^{2} - z \jaclmbracketdz{l'}{m-1} \rho^{2} - 2m z^2 \jaclmbracket{l'}{m-1} \big) \nonumber \\
	&\quadtwo + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ (m-1)(m+1) \jaclm{l}{m} \jaclmbracket{l'}{m-1} \rho^{2m} - z \jaclm{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m} \nonumber \\
	&\quadfour + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m-1} \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ (m-1)(m+1) \jaclm{l}{m} \jaclmbracket{l'}{m-1} \rho^{2m} - d_{l',m-1} z \jaclm{l}{m} \jaclm{l'}{m} \rho^{2m} \nonumber \\
	&\quadfour + d_{l,m} d_{l',m-1} \jaclmbracket{l}{m+1} \jaclm{l'}{m} \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ (m^2 - 1) \jaclm{l}{m} \big( \tilde \alpha_{l', m-1, 2} \jaclm{l'-1}{m} + \tilde \alpha_{l', m-1, 4} \jaclm{l'+1}{m} \big) \rho^{2m} \nonumber \\
	&\quadfour - d_{l',m-1} \jaclm{l}{m} \big( \tilde \gamma_{l',m,1} \jaclm{l'-1}{m} + \tilde \gamma_{l',m,2} \jaclm{l'+1}{m} \big) \rho^{2m} \nonumber \\
	&\quadfour + d_{l,m} d_{l',m-1} \jaclm{l'}{m} \big( \tilde \alpha_{l, m+1, 1} \jaclm{l-1}{m} + \tilde \alpha_{l, m+1, 3} \jaclm{l+1}{m} \big) \rho^{2m} \Big\} \: \D z \nonumber \\
	&= {\delta_{l',l-1} \over 2\pi} \Big\{ \big[ (m^2 - 1) \tilde \alpha_{l-1, m-1, 4} - d_{l-1,m-1} \tilde \gamma_{l-1,m,2} \big] {1 \over (\clm)^2} + d_{l,m} d_{l-1,m-1} {\tilde \alpha_{l-1, m-1, 1} \over (c_{l-1}^m)^2} \Big\} \nonumber \\
	&\quadtwo + {\delta_{l',l+1} \over 2\pi} \Big\{ \big[ (m^2 - 1) \tilde \alpha_{l+1, m-1, 2} - d_{l+1,m-1} \tilde \gamma_{l+1,m,1} \big] {1 \over (\clm)^2} \nonumber \\
	&\quadeight + d_{l,m} d_{l+1,m-1} {\tilde \alpha_{l-1, m-1, 3} \over (c_{l+1}^m)^2} \Big\}. \label{eqn:lemmaVSHrecurrencesproof2}
}
As we can see, the coefficients are then also only possibly nonzero for $l' = l \pm 1$. Combining the above with the \bsrefeqn{eqn:lemmaVSHrecurrencesproof}, we have that our two coefficients for $\calA_{l-1,m-1}, \calA_{l+1,m-1}$ are those stated in the Lemma as $A_{l,m,1}$ and $A_{l,m,3}$, for $m > 0$.

Next, assume $m \ge 0$ and consider the case $m' = m + 1$. The integral in \bsrefeqn{eqn:lemmaVSHrecurrencesproof} is then:
\bseqnnumber{
	&\int_{-1}^{1} \Big\{ m(m+1) \jaclm{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m} (1 + z^2) - m z \jaclm{l}{m} \jaclmbracketdz{l'}{m+1} \rho^{2m+2} \nonumber \\
	&\quadtwo \quad - (m+1) z \jaclmdz{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m+2} + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m+1} \rho^{2m+4} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ m(m+1) \jaclm{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m} (1 + z^2) \nonumber \\
	&\quadfour - (m+1) z \jaclmdz{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m+2} \nonumber \\
	&\quadfour + m \jaclmbracket{l'}{m+1} \rho^{2m} \big( - 2(m+1) z^2 \jaclm{l}{m} + \jaclm{l}{m} \rho^{2} - z \jaclmdz{l}{m} \rho^{2} \big) \nonumber \\
	&\quadfour + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m+1} \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ m(m+2) \jaclm{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m+2} - z \jaclmdz{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m+2} \nonumber \\
	&\quadfour + \jaclmdz{l}{m} \jaclmbracketdz{l'}{m+1} \rho^{2m+4} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ m(m+2) \jaclm{l}{m} \jaclmbracket{l'}{m+1} \rho^{2m+2} - d_{l,m} z \jaclmbracket{l}{m+1} \jaclmbracket{l'}{m+1} \rho^{2m+2} \nonumber \\
	&\quadfour + d_{l,m} d_{l',m+1} \jaclmbracket{l}{m+1} \jaclmbracket{l'}{m+2} \rho^{2m+4} \Big\} \: \D z \nonumber \\
	&= \int_{-1}^{1} \Big\{ m(m+2) \jaclmbracket{l'}{m+1} \big( \tilde \alpha_{l, m, 2} \jaclmbracket{l-1}{m+1} + \tilde \alpha_{l, m, 4} \jaclmbracket{l+1}{m+1} \big) \rho^{2m+2} \nonumber \\
	&\quadtwo - d_{l,m} \jaclmbracket{l'}{m+1} \big( \tilde \gamma_{l,m+1,1} \jaclmbracket{l-1}{m+1} + \tilde \gamma_{l,m+1,2} \jaclmbracket{l+1}{m+1} \big) \rho^{2m+2} \nonumber \\
	&\quadtwo + d_{l,m} d_{l',m+1} \jaclmbracket{l}{m+1} \big( \tilde \alpha_{l', m+2, 1} \jaclmbracket{l'-1}{m+1} + \tilde \alpha_{l', m+2, 3} \jaclmbracket{l'+1}{m+1}  \big) \rho^{2m+2} \Big\} \: \D z \nonumber \\
	&= {\delta_{l',l-1} \over 2\pi} \Big\{ \big[ m(m+2) \tilde \alpha_{l, m, 2} - d_{l,m} \tilde \gamma_{l,m+1,1} \big] {1 \over (c_{l-1}^{m+1})^2} + d_{l,m} d_{l-1,m+1} {\tilde \alpha_{l-1, m+2, 3} \over (c_{l}^{m+1})^2} \Big\} \nonumber \\
	&\quadtwo + {\delta_{l',l+1} \over 2\pi} \Big\{ \big[ m(m+2) \tilde \alpha_{l, m, 4} - d_{l,m} \tilde \gamma_{l,m+1,2} \big] {1 \over (c_{l-1}^{m+1})^2} + d_{l,m} d_{l+1,m+1} {\tilde \alpha_{l+1, m+2, 1} \over (c_{l}^{m+1})^2} \Big\}. \label{eqn:lemmaVSHrecurrencesproof3}
}
Again, we can see that the coefficients are then also only possibly nonzero for $l' = l \pm 1$. Combining the above with the \bsrefeqn{eqn:lemmaVSHrecurrencesproof}, we have that our two coefficients for $\calA_{l-1,m-1}, \calA_{l+1,m-1}$ are those stated in the Lemma as $A_{l,m,2}$ and $A_{l,m,4}$, for $m \ge 0$.

@@

	&\quadtwo \cdot \Big( \int_{-1}^{1} \rho(z)^{\abs{m} + \abs{m'} - 1} \Big\{ i m' \jaclmabs{l'}{m'}(z) \big[ \abs{m} z \jaclmabs{l}{m}(z) - \rho(z)^2 \jaclmabsdz{l}{m}(z) \big] \nonumber \\
	&\quadfour + i m \jaclmabs{l}{m}(z) \big[ \abs{m'} z \jaclmabs{l'}{m'}(z) - \rho(z)^2 \jaclmabs{l'}{m'}(z) \big] \Big\} \: \D z \Big) \nonumber \\

@@

	&\quadfour \cdot \Big( \int_{-1}^{1} \Big\{ \signfunc{m} 2 i \, m \, m' \, z \jaclmabs{l}{m} \jaclmabs{l'}{m'} \rho^{\abs{m} + \abs{m'} - 1} \nonumber \\

@@

since when the above is nonzero, $m, m'$ will have the same sign (or one is zero) and so $\abs{m}m' + \abs{m'}m = \signfunc{m}m\:m'$. Once again, we can conclude that $\calA^\perp_{l',m'}$ are zero for $m' \notin \{m-1, m+1\}$. It is left to evaluate the integral that is left at \bsrefeqn{eqn:lemmaVSHrecurrencesproof4} when $m'$ takes either $m\pm 1$ value. First, consider the case that $m > 0$ and $m' = m - 1$. The integral is then, using integration by parts:

@@

	&= \int_{-1}^{1} \Big\{ - 2 i \, m(m+1) \, z \jaclmabs{l}{m} \jaclmbracket{l'}{\abs{m} - 1} \rho^{2 \abs{m} - 2} \nonumber \\
	&\quadfour - i m \jaclmabs{l}{m} \jaclmbracketdz{l'}{\abs{m} - 1} \rho^{2\abs{m}} \nonumber \\

@@

	&\quadtwo \cdot \Big( \int_{-1}^{1} \Big\{ \big[ \abs{m} z \jaclmabs{l}{m}(z) - \rho(z)^2 \jaclmabsdz{l}{m}(z) \big] \nonumber \\
	&\quadeight \cdot \big[ \abs{m'} z \jaclmabs{l'}{m'}(z) - \rho(z)^2 \jaclmabs{l'}{m'}(z) \big] \nonumber \\

@@

\begin{figure}[tp]
	\centering % <-- added
	\centerline{\includegraphics[scale=0.6]{heat-eqn-alpha-0p0238-dt=0p01-nsteps=100}}
	\caption{Four snapshots of the solution $u$ of the heat equation with $\alpha = 1/42$ and a step size of $\Delta t = 0.01$, solved using the BDF2 timestepping method. Top Left: Initial conditions (0 timesteps). Top Right: After 25 timesteps. Bottom Left: After 50 timesteps. Bottom Right: After 75 timesteps.}
	\label{fig:heateqn}
\end{figure}

@@

\begin{figure}[tp]
	\centering % <-- added
	\centerline{\includegraphics[scale=0.6]{linear-swe-H=1-dt=0p01-nsteps=100}}
	\caption{Four snapshots of the solution for the height $h$ of the linearised shallow water equations with $\rotrate = \calH = 1$ and a step size of $\Delta t = 0.01$, solved using the backwards Euler timestepping method. Top Left: Initial conditions (0 timesteps). Top Right: After 50 timesteps. Bottom Left: After 75 timesteps. Bottom Right: After 100 timesteps.}
	\label{fig:swe}
\end{figure}
